---
title: "Developing Data Products Course Assignment"
author: "Chris Robertson"
date: "16th December 2019"
output: ioslides_presentation
---

<style>
pre {
  font-size: 15px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(shiny)
library(tidyverse)
library(tidyquant)
library(timetk)

```

## Introduction

This is a pitch presentation to support the Shiny application that enables users to model equity returns from a forecasted return and standard deviation. 

The Shiny application outputs:

- A histogram of forecasted returns with an optional density plot overlay
- A Monte Carlo simulation with the option to set the numer of simulations

The Shiny application can be found in:

https://chrisrobbo.shinyapps.io/DDP_Assignment1/

All code can be viewed in:

https://github.com/Robbocj01/DevelopingDataProducts


## Data for charts

Simulated monthly returns were generated using the rnorm function. The rnorm functions were given the number of points to generated, a forecasted return as mean and a forecasted standard deviation.

```{r simulated_rets, echo = TRUE}
        input_mean <- 1 / 120
        input_STDev <- 2 / 120
        input_no_points <- 1000
        
simulated_monthly_returns <- rnorm(input_no_points,
                                   input_mean,
                                   input_STDev)
head(simulated_monthly_returns, 5)
```

## Histogram

The first output from the application is a histogram of the simulated returns. In this example I have also chosen to overlay a density line.

```{r histogram_density,  echo = FALSE}
hist(simulated_monthly_returns, breaks = 40, col = 'darkgray', 
     border = 'white', main = "Histogram of Equity Index Returns",
     xlab = "Returns", prob = TRUE)
lines(density(simulated_monthly_returns), col = "blue", lwd=4)
```

## Monte Carlo Simulation

The second output is a monet carlo simulation. I have used 20 simulations in this example.

``` {r monte_carlo, echo = FALSE,  warning=FALSE, message = FALSE}
        input_mean <- 1 / 120
        input_STDev <- 2 / 120
        input_sims <- 20
        
        # Runs the returns simulationa and creates an index of returns
        simulation_accum_1 <- function(init_value, N, mean, stdev) {
            tibble(c(init_value, 1 + rnorm(N, mean, stdev))) %>% 
                `colnames<-`("returns") %>%
                mutate(growth = 
                           accumulate(returns, 
                                      function(x, y) x * y)) %>% 
                select(growth)
        }
        
        # Creates the dataframe ot capture the simulated returns
        starts <- 
            rep(1, input_sims) %>%
            set_names(paste("sim", 1:input_sims, sep = ""))
        
        # Naps the monte carlo simulation
        monte_carlo_sim <- 
            map_dfc(starts, 
                    simulation_accum_1, 
                    N = 120, 
                    mean = input_mean, 
                    stdev = input_STDev)
        
        
        monte_carlo_sim <- 
            monte_carlo_sim %>% 
            mutate(month = seq(1:nrow(.))) %>% 
            select(month, everything()) %>% 
            `colnames<-`(c("month", names(starts))) %>% 
            mutate_all(funs(round(., 2)))
        
        
        # Plots the results using ggplot
        monte_carlo_sim %>% 
            gather(sim, growth, -month) %>% 
            group_by(sim) %>% 
            ggplot(aes(x = month, y = growth, color = sim)) + 
            geom_line() +
            theme(legend.position="none")+
            ggtitle("Monte Carlo Simulation of Returns")+
            xlab("Month") + ylab("Growth of $1")+
            theme(plot.title = element_text(hjust = 0.5))


```
